---
title: "Mauna Loa"
author: "Faithwin Gbadamosi"
format: html
editor: visual
---

Load the necessary libraries

```{r}
library(readr) 
library(ggplot2) 
library(knitr) 
library(dplyr)
```

library(readr) library(ggplot2) library(knitr) library(dplyr)

# URL of the dataset

```{r}
url <- "ftp://aftp.cmdl.noaa.gov/products/trends/co2/co2_annmean_mlo.txt"
```

# Read the data

```{r}
co2_data <- read_table(url, skip = 57, col_names = c("Year", "Mean_CO2"))
```

co2_data \<- read_table(url, skip = 57, col_names = c("Year", "Mean_CO2"))

# View the first rows of the dataset using

```{r}
head(co2_data)
```

### Create a Time Series Plot of CO2 Levels

Plot to visualize how CO2 levels have changed over the years.



```{r}
ggplot(co2_data, aes(x = Year, y = Mean_CO2)) + geom_line(color = "blue") + labs(title = "Mauna Loa CO2 Annual Mean", x = "Year", y = "Mean CO2 (ppm)") + theme_minimal()

```

### Step 6: Generate a Summary Table

Summary table of CO2 data. Calculate the average CO2 level for each decade.



```{r}
co2_decade <- co2_data %>% mutate(Decade = floor(Year / 10) * 10) %>% group_by(Decade) %>% summarize(Mean_CO2 = mean(Mean_CO2, na.rm = TRUE))
```

# Display the summary table

```{r}
co2_decade %>% kable(caption = "Mean CO2 Levels per Decade")
```
